### 2021-04-14 priority-gv.tex
Change layout of echo server.

\subsubsection*{Progress and deadlock freedom}
PGV satisfies progress, as PGV configurations either reduce or are in normal form. However, the normal forms may seem surprising at first, as evaluating a well-typed PGV term does not necessarily produce \emph{just} a value. If a term returns an endpoint, then its normal form contains a thread which is ready to communicate on the dual of that endpoint. This behaviour is not new to PGV. Let us consider an example, adapted from Lindley and Morris~\cite{lindleymorris15}, in which a term returns an endpoint linked to an echo server. The echo server receives a value and sends it back unchanged:
\[
  \tm{\echo_x} \defeq \tm{\letpair{y}{x}{\recv\;{x}}{\letbind{x}{\send\;\pair{y}{x}}{\close\;x}}}
\]
Consider the program which creates a new channel, with endpoints $\tm{x}$ and $\tm{x'}$, spawns off an echo server listening on $\tm{x'}$, and then returns $\tm{x}$:
\[
  \tm{\main\;\letpair{x}{x'}{\new}{\andthen{\spawn\;(\lambda\unit.\echo_{x'})}}{x}}
\]
If we reduce the above program, we get $\tm{\res{x}{x'}{(\ppar{\main\;x}{\child\;\echo_{x'}})}}$. Clearly, no more evaluation is possible, even though the configuration contains the thread $\tm{\child\;\echo_{x'}}$, which is blocked on $\tm{x'}$. In~\cref{cor:pgv-closed-progress} we will show that if a term does not return an endpoint, it must produce \emph{only} a value.

>>>>

\subsubsection*{Progress and deadlock freedom}
PGV satisfies progress, as PGV configurations either reduce or are in normal form. However, the normal forms may seem surprising at first, as evaluating a well-typed PGV term does not necessarily produce \emph{just} a value. If a term returns an endpoint, then its normal form contains a thread which is ready to communicate on the dual of that endpoint. This behaviour is not new to PGV. Let us consider an example, adapted from Lindley and Morris~\cite{lindleymorris15}, in which a term returns an endpoint linked to an echo server. The echo server receives a value and sends it back unchanged. Consider the program which creates a new channel, with endpoints $\tm{x}$ and $\tm{x'}$, spawns off an echo server listening on $\tm{x}$, and then returns $\tm{x'}$:
\[
  \begin{array}{ll}
    \tm{\main}
    & \tm{\letpair{x}{x'}{\new}{}}
    \\
    & \tm{\andthen{\spawn\;(\lambda\unit.\echo_{x})}{x'}}
  \end{array}
  \hfill
  \begin{array}{lcl}
    \tm{\echo_x}
    & \defeq
    & \tm{\letpair{y}{x}{\recv\;{x}}{}}
    \\
    &
    & \tm{\letbind{x}{\send\;\pair{y}{x}}{\close\;x}}
  \end{array}
  \hfill
\]
If we reduce the above program, we get $\tm{\res{x}{x'}{(\ppar{\child\;\echo_{x}}{\main\;x'})}}$. Clearly, no more evaluation is possible, even though the configuration contains the thread $\tm{\child\;\echo_{x}}$, which is blocked on $\tm{x}$. In~\cref{cor:pgv-closed-progress} we will show that if a term does not return an endpoint, it must produce \emph{only} a value.
